---
title: |
       | Rats or Cats which sleeps longer?
       | SOLUTIONS
author: "Yu Zhang"
date: " `r Sys.Date()` "
output: 
  pdf_document: default
  html_document: default
  word_document:
  fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

In this analysis, we will address the question of whether rats (Rodentia) and cats (Carnivora) have similar number of sleep hours. 

# Data

The data is contained in the `msleep` dataset in the `tidyverse` package. This is loaded:

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
data("msleep")
#msleep
```

The data consists of `r nrow(msleep)` Species with `r ncol(msleep)` variables measured on it. 

# Filter data

We are only interested in the variables:

- **order:** which is a categorical nominal variable and gives the Order of the Species. 
- **sleep_total:** which is a quantitative continuous variable and gives the total amount of sleep in hours. 

As well, we are only interested in Species that are in the order Carnivora or Rodentia. The following code filters the dataset:

```{r}
rats_cats  <- msleep %>% 
  filter(order %in% c("Carnivora", "Rodentia")) %>% 
  select(order, sleep_total)
```

# Basic summary statistics

Table \ref{tab:s3} gives the summary statistics for each group. 

```{r, echo = FALSE}
rats_cats %>% 
  select(order) %>% 
  table() %>%
  knitr::kable(caption = "Frequency table of Order")

rats_cats %>% 
  select(sleep_total) %>%
  summary() %>%
  knitr::kable(caption = "Summary of sleep total\\label{tat:s2}")

rats_cats %>% 
  group_by(order) %>% 
  summarise(n = n(), 
            mean = mean(sleep_total), 
            sd = sd(sleep_total)) %>% 
  knitr::kable(caption = "Summary statistics for each Order\\label{tab:s3}")
```

# Side-by-side boxplots

Figure \ref{fig:boxplot} gives the side-by-side boxplots of sleep total for each order. 

```{r, fig.cap="Side-by-side boxplots of total sleep for each order.\\label{fig:boxplot}", echo = FALSE}
ggplot(rats_cats, aes(x = order, y = sleep_total, fill = order)) + 
  geom_boxplot(show.legend = FALSE)
```


# Two-sample t-test

The sample mean for each group was used. To recap the sample mean for each group is 

$$
\bar{Y}_i = \sum^{n_i}_{i = 1}Y_{ij},
$$
where $n_i$ is the number in the $i$th group, and $Y_{ij}$ is the $j$th observation in the $i$th group. 

The appropriate null and alternative hypotheses are

$$
\begin{aligned}
H_0 &: \mu_1 - \mu_2 = 0,\\
H_a &: \mu_1 - \mu_2 \ne 0,
\end{aligned}
$$
where $\mu_1$ is the mean of Carnivora and $\mu_2$ is the mean of Rodentia.

The test statistic is given by

$$
T=\frac{\bar{Y}_1 - \bar{Y}_2 - (\mu_1-\mu_2)}{\sqrt{\frac{S_1^2}{n_1} + \frac{S_2^2}{n_2}}}
$$

We perform a two-sample t-test with 

```{r t_test}
rats_cats_t <- with(rats_cats, t.test(sleep_total ~ order))
```

```{r t-test_print, echo=F}
rats_cats_t %>% print()
```

# Conclusion

The 95% confidence interval for the mean difference is (`r rats_cats_t$conf.int[1] %>% round(2)`, `r rats_cats_t$conf.int[2] %>% round(2)`), with a P-value `r rats_cats_t$p.value %>% round(4)`.

Hence, there is insufficient evidence to reject $H_0$.

# Session info

```{r session}
sessionInfo()
```

